Commit Rater

### 2015-08-24 presentations/paper/methodology.tex
Add TODOs to Data Analysis

\subsection{Data extraction}

This metamodel is concerned with MSR papers. Thus, the methodology
section would be reasonably subdivided into the three major phases of
an MSR research project.

The subsection on data extraction is concerned with issues like the
following:

\begin{itemize}
\item What repository was chosen and why?
\item What sort of extraction techniques is applied?
\item What sort of extra processing (e.g., filtering) is applied?
\item What constraints were chosen to help with scalability?
\end{itemize}

\subsection{Data synthesis}

Even the simplest MSR project carries out synthesis; data analysis (see
below) may not be carried out in all the cases. The subsection on data
synthesis is concerned with issues like the following:

\item What metrics are used?

\item What machine learning techniques are used?

\item What information retrieval techniques are used?

The typical MSR paper picks either metrics or machine learning or IR.

\subsection{Data analysis}

>>>>

\subsection{Data Extraction}

% This metamodel is concerned with MSR papers. Thus, the methodology
% section would be reasonably subdivided into the three major phases of
% an MSR research project.
%
% The subsection on data extraction is concerned with issues like the
% following:
%
% \begin{itemize}
% \item What repository was chosen and why?
% \item What sort of extraction techniques is applied?
% \item What sort of extra processing (e.g., filtering) is applied?
% \item What constraints were chosen to help with scalability?
% \end{itemize}

% TODO: Describe extraction process
% TODO: Describe preprocessing and output
% TODO: Mention commit-limit
% TODO: Introduce example repos

\subsection{Data Synthesis}

% Even the simplest MSR project carries out synthesis; data analysis (see
% below) may not be carried out in all the cases. The subsection on data
% synthesis is concerned with issues like the following:
%
% \begin{itemize}
%
% \item What metrics are used?
%
% \item What machine learning techniques are used?
%
% \item What information retrieval techniques are used?
%
% \end{itemize}
%
% The typical MSR paper picks either metrics or machine learning or IR.

% TODO: Describe general synthesis process, focusing on input and output
% TODO: List all criteria with details
% TODO: Try to express criteria as metrics
% TODO: Put special focus on those Natural Language Processing
% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation

\subsection{Data Analysis}
